Improving Day Ahead Electricity Load Forecasts with Google Trends

### 2014-07-30 Paper/DraftPaper.Rnw
Changed everything to AR(1).  This broke the stargazer reporting in appendix and drop all forward forecasting is not quite drop all forward.  The last is the last of the current model.

@@

<<echo=false,results=hide>>=
HourModelForecastCheck<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}

SAResults<-lapply(1:24, FUN = function(x)  lm(HourModelForecastCheck(x), data=WTrends))

@@

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
@
\end{center}
\end{figure}

@@

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
@
\end{center}
\end{figure}

@@

GrossTrends<-lapply(1:24, FUN = function(x)  lm(HourModel(x), data=WTrends))
@

@@

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Confidence Interval")
@
\end{center}
\end{figure}

@@

OneForwardError<-function(formula, nData){
  model<-lm(formula, data=WTrendsLimited[1:nData,], y=TRUE)
  modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
  predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)
}

@@

<<echo=false,results=tex>>=
News<-lm(HE19~F19+NewsTrends,data=WTrends)
# Oh, that works too
Gas<-lm(HE19~F19+GasTrends,data=WTrends)
# Gas does not
Traffic<-lm(HE19~F19+TrafficTrends,data=WTrends)
# Traffic does not
Restaurant<-lm(HE19~F19+RestaurantTrends,data=WTrends)
# Restaurant does not
Movie<-lm(HE19~F19+MovieTrends,data=WTrends)
# Snort...Movie does.  Cool place to be.
library(stargazer)
stargazer(News,Gas,Traffic,Restaurant,Movie,title="Alternate Google Search Models for Hour 19",column.labels=c("News","Gas","Traffic","Restaurant","Movie"), dep.var.caption="Hour 19 Load",dep.var.labels.include = FALSE)
@

@@

<<echo=false,results=tex>>=

for(x in 1:12){
  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
}
@
\clearpage

<<echo=false, results=tex>>=
for(x in 13:24){
  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
}
@

>>>>

#Get rid of the zero forecast in hour two
WTrends$F02[WTrends$F02==0]<-NA

@@

<<echo=false,results=hide>>=
library(nlme)
HourModelForecastCheck<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}

SAResults<-lapply(1:24, FUN = function(x)  gls(HourModelForecastCheck(x), data=WTrends,corAR1(form=~1),na.action=na.omit))

@@

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
@
\end{center}
\end{figure}

@@

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
@
\end{center}
\end{figure}

@@

GrossTrends<-lapply(1:24, FUN = function(x)  gls(HourModel(x), data=WTrends,corAR1(form=~1),na.action=na.omit))
@

@@

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=(LowInter+HighInter)/2, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Confidence Interval")
@
\end{center}
\end{figure}

@@

OneForwardError<-function(formula, nData){
  model<-gls(formula, data=WTrendsLimited[1:nData,],corAR1(form=~1),na.action=na.omit)
#   modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
#   predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)

tail(resid(model),1)

}

@@

<<echo=false,results=tex>>=
News<-gls(HE19~F19+NewsTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
# Oh, that works too
Gas<-gls(HE19~F19+GasTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
# Gas does not
Traffic<-gls(HE19~F19+TrafficTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
# Traffic does not
Restaurant<-gls(HE19~F19+RestaurantTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
# Restaurant does not
Movie<-gls(HE19~F19+MovieTrends,data=WTrends,corAR1(form=~1),na.action=na.omit)
# Snort...Movie does.  Cool place to be.
library(stargazer)
stargazer(News,Gas,Traffic,Restaurant,Movie,title="Alternate Google Search Models for Hour 19",column.labels=c("News","Gas","Traffic","Restaurant","Movie"), dep.var.caption="Hour 19 Load",dep.var.labels.include = FALSE)
@

@@

<<echo=false,results=tex>>=
# 
# for(x in 1:12){
#   stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
# }
@
\clearpage

<<echo=false, results=tex>>=
# for(x in 13:24){
#   stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
# }
@
